|

### 2023-01-17 RR_manuscript/supplementary_materials.Rmd
include sankey plot in supplementary materials

---
title: "Supplementary materials"
output: pdf_document
date: "`r Sys.Date()`"
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = here::here())
library("dplyr")
library("ggplot2")
library("tidyr")
library("readr")
library("googlesheets4")
library("glue")
library("here")
library("fs")
library("forcats")
library("purrr")
library("stringr")
library("kableExtra")
```

@@

# Read in google sheet and join it with review data and phd/prior belief
# data
msa_models_unique <- left_join(
  read_sheet(the_sheet) %>% 
    filter(added_on_osf == "yes") %>% 
    select(
      animal, model_n, outcome, typicality_operationalization, 
      framework, model, temporal_window, random_effects, n_random, 
      n_predictors, operationalisation, n_terms, n_coefficients, n_random_int, 
      n_random_slo, n_random_smooth, n_models
      ) %>%
    distinct(), 
  readRDS("./data/peer_review/msa_reviews.rds") %>% 
    select(animal = Q3, phon_rating = Q5_2, stat_rating = Q5_3, 
           all_rating = Q5_4) %>% 
    group_by(animal) %>% 
    # Remove ratings from 2 teams that dropped
    filter(!(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
    summarize(phon_rating = median(phon_rating), 
              stat_rating = median(stat_rating), 
              all_rating = median(all_rating)), 
  by = "animal"
) %>% 
  left_join(., 
    read_csv("./data/questionnaires/msa_intake_form_untidy.csv") %>%
      filter(added_on_osf == "yes", 
        !(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
      select(animal, years_from_phd, prior_belief), 
    by = "animal"
  )

>>>>

---
title: |
  Multidimensional signals and analytic flexibility:  
  Estimating degrees of freedom in human speech analyses
subtitle: "Supplementary materials"
author: |
  Initiating authors:  
  Stefano Coretta, Joseph V. Casillas, and Timo Roettger
output: pdf_document
date: "`r Sys.Date()`"
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library("dplyr")
library("ggplot2")
library("tidyr")
library("readr")
library("googlesheets4")
library("glue")
library("here")
library("fs")
library("forcats")
library("purrr")
library("stringr")
library("kableExtra")
```

```{r}
#| label: sankey-plot
#| fig.cap: "Sankey plot illustrating workflow choices from analyst teams."
#| out.width: "100%"
knitr::include_graphics(path = here("figs", "flow_outcome.png"))
```

@@

# Read in google sheet and join it with review data and phd/prior belief
# data
msa_models_unique <- left_join(
  read_sheet(the_sheet) %>% 
    filter(added_on_osf == "yes") %>% 
    select(
      animal, model_n, outcome, typicality_operationalization, 
      framework, model, temporal_window, random_effects, n_random, 
      n_predictors, operationalisation, n_terms, n_coefficients, n_random_int, 
      n_random_slo, n_random_smooth, n_models
      ) %>%
    distinct(), 
  readRDS(here("./data/peer_review/msa_reviews.rds")) %>% 
    select(animal = Q3, phon_rating = Q5_2, stat_rating = Q5_3, 
           all_rating = Q5_4) %>% 
    group_by(animal) %>% 
    # Remove ratings from 2 teams that dropped
    filter(!(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
    summarize(phon_rating = median(phon_rating), 
              stat_rating = median(stat_rating), 
              all_rating = median(all_rating)), 
  by = "animal"
) %>% 
  left_join(., 
    read_csv(here("./data/questionnaires/msa_intake_form_untidy.csv")) %>%
      filter(added_on_osf == "yes", 
        !(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
      select(animal, years_from_phd, prior_belief), 
    by = "animal"
  )
